---
output: html_document
---
#Air Quality vs. Individuals diagnosed with Asthma 
#Vincent Chou [vchou2@ucmerced.edu]
#December 12-2014
#Plots of the mean and max air particle vs. individuals with Asthma in SJV and the individuals diagnosed over the years in each county. 

```{r}
setwd("~/ENVE105/Project")

Asthma <- read.csv("asthma_count.csv")
Asthmac <- read.csv("Data_203204.csv")
Air<- read.csv("SJCABPM25.csv")


summary(Asthma)
summary(Air)
str(Asthma)
str(Air)
# 
# Kings<- Air[which(Air$COUNTY.NAME=="Kings"),]
# strDatesKings<- c("01/15/2001","12/12/2010")
# Kingsformat<- "%y"
# Kings$date<-as.Date(Kings$DATE,Kingsformat)
# 
# plot(Kings$PM25_CONCENTRATION~Kings$date,main="Concentration in Kings vs. time", xlab="Date", ylab="PM_25 Conentration")
# 
# 
# plot(Asthma$Year,Asthma$Kings,main="Kings vs.Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
# 
# lines(Asthma$Year,Asthma$Kings,type="b",lwd=1.5)
# 
# hist(Kings$PM25_CONCENTRATION,main="Conentration",xlab="Concentration range",ylab="Frequency")
# 
# ```
# 
# ```{r}
# Fresno<- Air[which(Air$COUNTY.NAME=="Fresno"),]
# strDatesFresno<- c("01/15/2001","12/12/2010")
# datesKings<- as.Date(strDatesKings,"%m/%d/%y")
# Kingsformat<- "%y/%m"
# Kings$date<-as.Date(Kings$DATE,Kingsformat)
# 
# plot(Fresno$PM25_CONCENTRATION~Fresno$DATE,main= "Concentration in Fresno vs.time", xlab="Date",ylab="PM_25 Conentration")
# 
# lines(Fresno$PM25_CONCENTRATION~Fresno$DATE, type="b",lwd=1.5)
# 
# plot(Asthma$Year, Asthma$Fresno,main="Fresno vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
# 
# lines(Asthma$Year,Asthma$Fresno,type="b",lwd=1.5)
# 
# hist(Fresno$PM25_CONCENTRATION, main="Concentration",xlab="Concentration range",ylab="Frequency")
# ```
# 
# ```{r}
# Kern<- Air[which(Air$COUNTY.NAME=="Kern"),]
# 
# plot(Kern$PM25_CONCENTRATION~Kern$DATE, main= "Concentration in Kern vs.time", xlab="Date",ylab="PM_25 Conentration")
# 
# lines(Kern$PM25_CONCENTRATION~Kern$DATE, type="b",lwd=1.5)
# 
# plot(Asthma$Year, Asthma$Kern,main="Kern vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
# 
# lines(Asthma$Year,Asthma$Kern,type="b",lwd=1.5)
# 
# hist(Kern$PM25_CONCENTRATION, main="Concentration",xlab="Concentration range",ylab="Frequency")
# ```
# 
# ```{r}
# Merced<- Air[which(Air$COUNTY.NAME=="Merced"),]
# 
# plot(Merced$PM25_CONCENTRATION~Merced$DATE, main= "Concentration in Merced vs.time", xlab="Date",ylab="PM_25 Conentration")
# 
# lines(Merced$PM25_CONCENTRATION~Merced$DATE, type="b",lwd=1.5)
# 
# plot(Asthma$Year, Asthma$Merced,main="Merced vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
# 
# lines(Asthma$Year,Asthma$Merced,type="b",lwd=1.5)
# 
# hist(Merced$PM25_CONCENTRATION, main="Concentration", xlab="Concentration range", ylab="Frequency")
# ```
# 
# ```{r}
# Stanislaus<- Air[which(Air$COUNTY.NAME=="Stanislaus"),]
# 
# plot(Stanislaus$PM25_CONCENTRATION~Stanislaus$DATE, main= "Concentration in Stanislaus vs.time", xlab="Date",ylab="PM_25 Conentration")
# 
# lines(Stanislaus$PM25_CONCENTRATION~Stanislaus$DATE, type="b",lwd=1.5)
# 
# plot(Asthma$Year, Asthma$Stanislaus,main="Stanislaus vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
# 
# lines(Asthma$Year,Asthma$Stanislaus,type="b",lwd=1.5)
# 
# hist(Stanislaus$PM25_CONCENTRATION, main="Concentration",xlab="Concentration range", ylab="Frequency")
# ```
# 
# ```{r}
#  Madera<- Air[which(Air$COUNTY.NAME=="Madera"),]
#  
# plot(Madera$PM25_CONCENTRATION~Madera$DATE, main= "Concentration in Madera vs.time", xlab="Date",ylab="PM_25 Conentration")
#  
# lines(Madera$PM25_CONCENTRATION~Madera$DATE, type="b",lwd=1.5)
#  
# plot(Asthma$Year, Asthma$Madera,main="Madera vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
#  
# lines(Asthma$Year,Asthma$Madera,type="b",lwd=1.5)
# 
# hist(Madera$PM25_CONCENTRATION, main="Concentration", xlab="Concentration range", ylab="frequency")
# ```
# 
# ```{r}
# Tulare<- Air[which(Air$COUNTY.NAME=="Tulare"),]
# 
# plot(Tulare$PM25_CONCENTRATION~Tulare$DATE, main= "Concentration in Tulare vs.time", xlab="Date",ylab="PM_25 Conentration")
# 
# lines(Tulare$PM25_CONCENTRATION~Tulare$DATE, type="b",lwd=1.5)
# 
# plot(Asthma$Year, Asthma$Tulare,main="Tulare vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
# 
# lines(Asthma$Year,Asthma$Tulare,type="b",lwd=1.5)
# 
# hist(Tulare$PM25_CONCENTRATION, main="Concentration", xlab="Concentration range", ylab="frequency")
# ```

```{rfig.width=10,fig.height=9}
#(mfrow=c(3,3));
plot(Asthma$Year, Asthma$Fresno,main="Fresno vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
lines(Asthma$Year,Asthma$Fresno,type="b",lwd=1.5)
plot(Asthma$Year, Asthma$Kern,main="Kern vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
lines(Asthma$Year,Asthma$Kern,type="b",lwd=1.5)
plot(Asthma$Year, Asthma$Kings,main="Kings vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
lines(Asthma$Year,Asthma$Kings,type="b",lwd=1.5)
plot(Asthma$Year, Asthma$Madera,main="Madera vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
lines(Asthma$Year,Asthma$Madera,type="b",lwd=1.5)
plot(Asthma$Year, Asthma$Merced,main="Merced vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals diagnosed with Asthma")
lines(Asthma$Year,Asthma$Merced,type="b",lwd=1.5)
plot(Asthma$Year, Asthma$Stanislaus,main="Stanislaus vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
lines(Asthma$Year,Asthma$Stanislaus,type="b",lwd=1.5)
plot(Asthma$Year, Asthma$Tulare,main="Tulare vs. Ind hospitalized with Asthma", xlab="Year", ylab="Number of individuals with Asthma")
lines(Asthma$Year,Asthma$Tulare,type="b",lwd=1.5)
```

```{rfig.width=10,fig.height=9}
#par(mfrow=c(3,3));

plot(Asthmac$Year, Asthmac$Fresno, main="Fresno", xlab="Time", ylab="Diagnosed per 10,000")
lines(Asthmac$Year, Asthmac$Fresno, type="b",lwd=1.5)

plot(Asthmac$Year, Asthmac$Kern, main="Kern", xlab="Time", ylab="Diagnosed per 10,000")
lines(Asthmac$Year, Asthmac$Kern, type="b",lwd=1.5)

plot(Asthmac$Year, Asthmac$Kings, main="Kings", xlab="Time", ylab="Diagnosed per 10,000")
lines(Asthmac$Year, Asthmac$Kings, type="b",lwd=1.5)

plot(Asthmac$Year, Asthmac$Madera, main="Madera", xlab="Time", ylab="Diagnosed per 10,000")
lines(Asthmac$Year, Asthmac$Madera, type="b",lwd=1.5)

plot(Asthmac$Year, Asthmac$Merced, main="Merced", xlab="Time", ylab="Diagnosed per 10,000")
lines(Asthmac$Year, Asthmac$Merced, type="b",lwd=1.5)

plot(Asthmac$Year, Asthmac$SanLuisObispo, main="SLO", xlab="Time", ylab="Diagnosed per 10,000")
lines(Asthmac$Year, Asthmac$SanLuisObispo, type="b",lwd=1.5)

plot(Asthmac$Year, Asthmac$Stanislaus, main="Stanislaus", xlab="Time", ylab="Diagnosed per 10,000")
lines(Asthmac$Year, Asthmac$Stanislaus, type="b",lwd=1.5)

plot(Asthmac$Year, Asthmac$Tulare, main="Fresno", xlab="Time", ylab="Diagnosed per 10,000")
lines(Asthmac$Year, Asthmac$Tulare, type="b",lwd=1.5)
```

```{r}
par(mfrow=c(1,2))
 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Fresno"))
   PMmeans<- c(PMmeans,mean(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,2])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgFresno<- as.data.frame(cbind(Year,PMmeans,Asthmarates))

 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Kern"))
   PMmeans<- c(PMmeans,mean(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,3])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgKern<- as.data.frame(cbind(Year,PMmeans,Asthmarates))

 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Kings"))
   PMmeans<- c(PMmeans,mean(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,4])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgKings<- as.data.frame(cbind(Year,PMmeans,Asthmarates))


 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Madera"))
   PMmeans<- c(PMmeans,mean(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,5])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgMadera<- as.data.frame(cbind(Year,PMmeans,Asthmarates))

 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Merced"))
   PMmeans<- c(PMmeans,mean(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,6])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgMerced<- as.data.frame(cbind(Year,PMmeans,Asthmarates))

 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Stanislaus"))
   PMmeans<- c(PMmeans,mean(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,2])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgStanislaus<- as.data.frame(cbind(Year,PMmeans,Asthmarates))

 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Tulare"))
   PMmeans<- c(PMmeans,mean(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,2])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgTulare<- as.data.frame(cbind(Year,PMmeans,Asthmarates))


Centralvalley<- rbind(BasinAvgFresno,BasinAvgKern,BasinAvgKings,BasinAvgMadera,BasinAvgMerced,BasinAvgStanislaus,BasinAvgTulare)

plot(Centralvalley$PMmeans,Centralvalley$Asthmarates,main="Air Quality vs. Asthma Rates",xlab="Annual Mean 2.5",ylab="Annual Asthma Hospitalization per 10,000")
centralline<- lm(Asthmarates~PMmeans,data=Centralvalley)
abline(centralline)
summary(centralline)


 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Fresno"))
   PMmeans<- c(PMmeans,max(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,2])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgFresno<- as.data.frame(cbind(Year,PMmeans,Asthmarates))

 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Kern"))
   PMmeans<- c(PMmeans,max(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,3])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgKern<- as.data.frame(cbind(Year,PMmeans,Asthmarates))

 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Kings"))
   PMmeans<- c(PMmeans,max(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,4])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgKings<- as.data.frame(cbind(Year,PMmeans,Asthmarates))


 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Madera"))
   PMmeans<- c(PMmeans,max(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,5])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgMadera<- as.data.frame(cbind(Year,PMmeans,Asthmarates))

 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Merced"))
   PMmeans<- c(PMmeans,max(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,6])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgMerced<- as.data.frame(cbind(Year,PMmeans,Asthmarates))

 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Stanislaus"))
   PMmeans<- c(PMmeans,max(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,2])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgStanislaus<- as.data.frame(cbind(Year,PMmeans,Asthmarates))

 Year <- c(2001:2011)
 PMmeans<- NULL
 Asthmarates<- NULL
 j <- 1
 for(i in seq(from=2001, to=2011, by=1)){
   airsubset<- subset(Air,(Air$year==i) & (Air$COUNTY.NAME=="Tulare"))
   PMmeans<- c(PMmeans,max(airsubset$PM25_CONCENTRATION,na.rm=TRUE))
   Asthmasum<- (Asthmac[j,2])
   j<- j+1
   Asthmarates<- c(Asthmarates,Asthmasum)
 }
BasinAvgTulare<- as.data.frame(cbind(Year,PMmeans,Asthmarates))


Centralvalley2<- rbind(BasinAvgFresno,BasinAvgKern,BasinAvgKings,BasinAvgMadera,BasinAvgMerced,BasinAvgStanislaus,BasinAvgTulare)

Centralvalley21<- subset(Centralvalley2,is.finite(Centralvalley2$PMmeans))

plot(Centralvalley21$PMmeans,Centralvalley21$Asthmarates,main="Air Quality vs. Asthma Rates",xlab="Annual max 2.5",ylab="Annual Asthma Hospitalization per 10,000")
centralline2<- lm(Asthmarates~PMmeans,data=Centralvalley21)
abline(centralline2)
summary(centralline2)